SMT-Boosted Security Types for Low-Level MPC

### 2025-04-26 esop25/slides.tex
checkpoint

  Low-level, probabilistic protocols are defined in terms of basic variable types
  (identifiers $x$ distinguish them):
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  We localize computation to \emph{clients}, and any information
  exchanged between clients must be through messaging.
  %\begin{exampleblock}{Toy Example:}
  %  $$
  %  \begin{array}{rcl@{\qquad}l}
  %    \mx{x}{1} &:=& \elab{(\secret{x} - \flip{x})}{2}  & \textit{(unicast)}\\
  %    \mx{y}{*} &:=& \elab{(\flip{y} + \mesg{x})}{1}  & \textit{(broadcast)}
  %  \end{array}
  %  $$ 
  %\end{exampleblock}
\end{frame}

@@

$$    
  \inferrule[Encode]
  {\eqs \models \phi \eop \phi' \oplus \rx{w}{\cid} \\
   \oplus \in \{ \fplus,\fminus \}\\
   \eqj{R}{\eqs}{\phi'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{\phi}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
$$

>>>>

  Low-level, probabilistic protocols are defined in terms of basic variable types
  (identifiers $x$ distinguish them):
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  \emph{Computations} are normal field operations on variables-- addition (+), multiplication (*),
  and additive inverse (-).

  We localize computation to \emph{clients}, and any information
  exchanged between clients must be through messaging.
  %\begin{exampleblock}{Toy Example:}
  %  $$
  %  \begin{array}{rcl@{\qquad}l}
  %    \mx{x}{1} &:=& \elab{(\secret{x} - \flip{x})}{2}  & \textit{(unicast)}\\
  %    \mx{y}{*} &:=& \elab{(\flip{y} + \mesg{x})}{1}  & \textit{(broadcast)}
  %  \end{array}
  %  $$ 
  %\end{exampleblock}
\end{frame}

@@

Verifying equational properties 
$$    
  \inferrule[Encode]
  {\eqs \models \phi \eop \phi' \oplus \rx{w}{\cid} \\
   \oplus \in \{ \fplus,\fminus \}\\
   \eqj{R}{\eqs}{\phi'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{\phi}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
$$
